DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-04-19 paper/comparison.tex
minor fixes

\begin{table*}[h]
  \centering
  \begin{adjustbox}{width=1\textwidth}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Item    & Raspberry Pi 3 (B)   & Intel UP                  & NVIDIA Jetson TX2\\
    \hline
            & BCM2837              & X5-Z8350 (Cherry Trail)   & Tegra X2 \\
    CPU     & 4x Cortex-A53@1.2GHz/512KB L2  &
              4x Atom@1.92GHz/2MB L2 &
              4x Cortex-A57@2GHz/2MB L2 \\
            &              &              & 2x Denver@2.0GHz/2MB L2 (not used)  \\
    \hline
    GPU     &  VideoCore IV (not used)    &
               Intel HD 400 Graphics (not used) &
               Pascal 256 CUDA cores   \\
    \hline
    Memory  & 1GB LPDDR2   &  2GB DDR3L     & 8GB LPDDR4              \\
    \hline
	Peak Memory Bandwidth & 8.5 GB/s & 12.8 GB/s & 59.7 GB/s \\
	\hline
	Measured Bandwidth & 2127.94 MB/s & 3951.94 MB/s & 4447.90 MB/s \\
	\hline
	Cost (\$) & 35 & 100 & 600 \\
	\hline
  \end{tabular}
  \end{adjustbox}
  \caption{Compared embedded computing platforms}
  \label{tbl:platforms}
\end{table*}

In this section, we compare three computing platforms---the Raspberry
Pi 3, the Intel UP~\footnote{http://www.up-board.org/up/} and the NVIDIA
Jetson
TX2~\footnote{http://www.nvidia.com/object/embedded-systems-dev-kits-modules.html}---from
the point of view of supporting end-to-end deep learning
based autonomous vehicles. 
Table~\ref{tbl:platforms} shows architectural features of the three
platforms~\footnote{The GPU of Intel UP and the two Denver cores in the
  Tegra TX2 are not used in evaluation due to TensorFlow issues.}.

>>>>

\begin{table*}[h]
  \centering
  \begin{adjustbox}{width=1\textwidth}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Item    & Raspberry Pi 3 (B)   & Intel UP                  & NVIDIA Jetson TX2\\
    \hline
            & BCM2837              & X5-Z8350 (Cherry Trail)   & Tegra X2 \\
    CPU     & 4x Cortex-A53@1.2GHz/512KB L2  &
              4x Atom@1.92GHz/2MB L2 &
              4x Cortex-A57@2.0GHz/2MB L2 \\
            &              &              & 2x Denver@2.0GHz/2MB L2 (not used)  \\
    \hline
    GPU     &  VideoCore IV (not used)    &
               Intel HD 400 Graphics (not used) &
               Pascal 256 CUDA cores   \\
    \hline
    Memory  & 1GB LPDDR2   &  2GB DDR3L     & 8GB LPDDR4              \\
    \hline
	Peak Memory Bandwidth & 8.5 GB/s & 12.8 GB/s & 59.7 GB/s \\
	%% \hline
	%% Measured Bandwidth & 2127.94 MB/s & 3951.94 MB/s & 4447.90 MB/s \\
	\hline
	Cost  & \$35 & \$100 & \$600 \\
	\hline
  \end{tabular}
  \end{adjustbox}
  \caption{Compared embedded computing platforms}
  \label{tbl:platforms}
\end{table*}

In this section, we compare three computing platforms---the Raspberry
Pi 3, the Intel UP~\cite{intelup} and the NVIDIA Jetson
TX2~\cite{nvidiajetson}---from the point of view of supporting
end-to-end deep learning based autonomous vehicles. 
Table~\ref{tbl:platforms} shows architectural features of the three
platforms~\footnote{The GPU of Intel UP and the two Denver cores in the
  Tegra TX2 are not used in evaluation due to TensorFlow issues.}.

### 2018-04-19 paper/related.tex
minor fixes

There are several relatively inexpensive RC-car based autonomous car
testbeds. MIT's RaceCar~\cite{shin2017project} and UPenn's
F1$/$10~\cite{upennf1tenth} are both based on a Trexx 1/10 scale RC
car and a powerful NVIDIA Jetson multicore computing platform, which
is equipped with many sophisticated sensor packages such as a lidar.
However, they both cost more than \$3,000, requiring considerable
investment. DonkeyCar~\cite{donkeycar} is similar to our DeepPicar as
it also uses a Raspberry Pi 3 and a similar CNN for end-to-end
control, although it costs more (about \$200).
%% because it uses a more
%% expensive 1/16 scale RC car than our 1/24 scale one.
The main contribution of our paper is in the detailed analysis of
computational aspects of executing a CNN-based real-time control
workload on diverse embedded computing platforms.

>>>>

There are several relatively inexpensive RC-car based autonomous car
testbeds. MIT's RaceCar~\cite{shin2017project} and UPenn's
F1$/$10~\cite{upennf1tenth} are both based on a Traxxas 1/10 scale RC
car and a NVIDIA Jetson multicore computing platform, which
is equipped with many sophisticated sensor packages such as a lidar.
However, they both cost more than \$3,000, requiring considerable
investment. DonkeyCar~\cite{donkeycar} is similar to our DeepPicar as
it also uses a Raspberry Pi 3 and a similar CNN for end-to-end
control, although it costs more (about \$200).
%% because it uses a more
%% expensive 1/16 scale RC car than our 1/24 scale one.
The main contribution of our paper is in the detailed analysis of
computational aspects of executing a CNN-based real-time control
workload on diverse embedded computing platforms.
